---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DRCdemand

<!-- badges: start -->
[![R-CMD-check](https://github.com/DylanDijk/DRCdemand/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/DylanDijk/DRCdemand/actions/workflows/R-CMD-check.yaml)
[![test-coverage](https://github.com/DylanDijk/DRCdemand/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/DylanDijk/DRCdemand/actions/workflows/test-coverage.yaml)
<!-- badges: end -->

The goal of DRCdemand is to aid in the analysis of the Irish electricity demand data set. Namely, we provide functions to perform clustering, forecasting and model aggregation.

## Installation

You can install the development version of DRCdemand from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("DylanDijk/DRCdemand")
```

## Example

This is a basic example which shows you how to compute Gower's dissimilarity matrix:

```{r example}
library(DRCdemand)
data <- data.frame(
  V1 = c(1, 2, 3),
  V2 = c(4, 5, 6),
  V3 = c(7, 8, 9),
  V4 = as.factor(c(1, 1, 2))
)
gowers_distance(data)
```

